Redshift evolution of the SN stretch distribution

### 2019-12-05 Nicolas.tex
Integrated plots and updates

\documentclass[bibnumber]{aa}

\usepackage{hyperref}

@@

%    \caption{(a) $z\St{max}$ determination from the magnitude limited data; (b) SDSS, %SNLS and PS1 samples cut at $z\St{max}$ as explained in
%    section \ref{sec:sam}. The data we use is in plain markers.}
%\end{figure*}

@@

We base our analysis on the latest SNe Ia compilation: the Pantheon catalog from
\cite{scolnic2018a}. Using this dataset, we aim at probing the evolution of the
distribution of SNe Ia stretch in nature as a function of redshift. Because the
observed magnitude of a SN Ia is correlated with its stretch and its color, in a
magnitude limited survey such as those consituing most of the Pantheon sample,
the distribution of these lightcurve parameters is not representative of the
true underlying distribution above a certain limiting redshift. The first SNe Ia
that such a survey will miss because they will be too faint are indeed the
reddest and the lowest-stretch SNe Ia. If such a selection effect is not
accounted for, we might confuse true population drift we selection function or
conversally.

@@

\mr{In Section~\ref{sec:testzmax}, we test the impact on using more conservative redshift limits ($z_{lim}=0.15$ for SDSS, $z_{lim}=0.27$ for PS and $z_{lim}=0.55$ for SNLS, following Fig.~14 of \citealt{perrett2010}). 
}

@@

We fitted it on SNf data, giving the results table \ref{tab:val}. For clarity
with the next models, we named it 3G2M2S$\St{SNf}$ for it has a total of 3
gaussians but with only 2 means and 2 standard deviations, and has been fitted
on SNf data only.

@@

@@

>>>>

\documentclass[]{aa} %bibnumber

%\usepackage{hyperref}
\usepackage{txfonts}
\usepackage{amsmath}
\usepackage[colorlinks,breaklinks]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue}

@@

%    \caption{(a) $z\St{max}$ determination from the magnitude limited data; (b) SDSS, %SNLS and PS1 samples cut at $z\St{max}$ as explained in
%    section \ref{sec:sam}. The data we use is in plain markers.}
%\subfigure[Method]{\label{fig:zdet}

%\end{figure*}

@@

We base our analysis on the latest SNe Ia compilation: the Pantheon catalog from
\cite{scolnic2018}. Using this dataset, we aim at probing the evolution of the
distribution of SNe Ia stretch in nature as a function of redshift. \mr{We thus have to }

Because the
observed magnitude of a SN Ia is correlated with its stretch and its color, in a
magnitude limited survey such as those consituing most of the Pantheon sample,
the distribution of these lightcurve parameters is not representative of the
true underlying distribution above a certain limiting redshift. The first SNe Ia
that such a survey will miss because they will be too faint are indeed the
reddest and the lowest-stretch SNe Ia. If such a selection effect is not
accounted for, we might confuse true population drift we selection function or
conversally.

@@

\mr{In Section~\ref{sec:testzmax}, we test the impact on using more conservative redshift limits ($z_{lim}=0.15$ for SDSS, $z_{lim}=0.27$ for PS and $z_{lim}=0.55$ for SNLS, following Fig.~14 of \citealt{perrett2010}).} The cuts on the raw data of those three samples are shown figure \red{fig:cuts}.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/hist_surveys_cuts.pdf}
    \caption{Histograms of the 3 surveys on which we applied cuts to get rid of selection effects, as discussed in section \ref{sec:sam}.}
    \label{fig:cuts}
\end{figure}

@@

We fitted it on SNf data, giving the results table \ref{tab:val}, with a graphical representation shown figure \ref{fig:snf_model}. For clarity
with the next models, we named it 3G2M2S$\St{SNf}$ for it has a total of 3
gaussians but with only 2 means and 2 standard deviations, and has been fitted
on SNf data only.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/stretchevol_model_maglim-cuts.pdf}
    \caption{Result of the model fitted on SNF data and mean of stretch and redshift of the other surveys used for this analysis. Conservative data is shown in transparent markers.}
    \label{fig:snf_model}
\end{figure}

@@

To test the coherence of this model, we also fitted it using all the data from the surveys indistinctly. These results are shown figures \ref{fig:model_all} and \ref{fig:model_all_cons}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/stretchevol_all_vs_snf_maglim_sup.pdf}
    \caption{Result of the model fitted on all surveys data cut at the non-conservative $z_{\mathrm{max}}$. We chose the bins to compute the means of stretch and redshift by making them equal in number of SNe Ia.}
    \label{fig:model_all}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/stretchevol_all_vs_snf_maglim_inf.pdf}
    \caption{Result of the model fitted on all surveys data cut at the conservative $z_{\mathrm{max}}$. We chose the bins to compute the means of stretch and redshift by making them equal in number of SNe Ia.}
    \label{fig:model_all}
\end{figure}

@@

\begin{acknowledgements}
    This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement n 759194 - USNAC). Support has been provided by the Institut Universitaire de France, the CNES, and the region Auvergne-Rhone-Alpes.
\end{acknowledgements}

\bibliographystyle{aa} % style aa.bst
\begin{thebibliography}{} 
% A
\bibitem[Abbott et al.(2018)]{abbott2018} Abbott, T.~M.~C., Abdalla, F.~B., Alarcon, A., et al.\ 2018, \prd, 98, 043526

\bibitem[Ata et al.(2017)]{ata2017} Ata, M., Kitaura, F.-S., Chuang, C.-H., et al.\ 2017, \mnras, 467, 3993

% B
% C
\bibitem[Chabanier et al.(2019)]{chabanier2019} Chabanier, S., Millea, M., \& Palanque-Delabrouille, N.\ 2019, \mnras, 489, 2247
\bibitem[Coles, \& Jones(1991)]{coles1991} Coles, P., \& Jones, B.\ 1991, \mnras, 248, 1

% D
% E
% F
\bibitem[Freedman et al.(2019)]{freedman2019} Freedman, W.~L., Madore, B.~F., Hatt, D., et al.\ 2019, \apj, 882, 34

% G

%\bibitem[Graziani et al.(2019)]{graziani2019} Graziani, R., Courtois, H.~M., Lavaux, G., et al.\ 2019, \mnras, 488, 5438

% H
% I 
% J
\bibitem[Jones et al.(2018)]{jones2018} Jones, D.~O., Riess, A.~G., Scolnic, D.~M., et al.\ 2018, \apj, 867, 108

% K

\bibitem[Knox, \& Millea(2019)]{knox2019} Knox, L., \& Millea, M.\ 2019, arXiv e-prints, arXiv:1908.03663

% L

% M
% N
% O
% P
\bibitem[Poulin et al.(2019)]{poulin2019} Poulin, V., Smith, T.~L., Karwal, T., et al.\ 2019, \prl, 122, 221301

\bibitem[Planck Collaboration et al.(2018)]{planck2018} Planck Collaboration, Aghanim, N., Akrami, Y., et al.\ 2018, arXiv e-prints, arXiv:1807.06209

% Q
% R
\bibitem[Reid et al.(2019)]{reid2019} Reid, M.~J., Pesce, D.~W., \& Riess, A.~G.\ 2019, arXiv e-prints, arXiv:1908.05625

\bibitem[Riess et al.(2016)]{riess2016} Riess, A.~G., Macri, L.~M., Hoffmann, S.~L., et al.\ 2016, \apj, 826, 56

\bibitem[Riess et al.(2019)]{riess2019} Riess, A.~G., Casertano, S., Yuan, W., et al.\ 2019, \apj, 876, 85

\bibitem[{Rigault {et~al.}(2013)}]{rigault2013}
Rigault, M., Copin, Y., Aldering, G., {et~al.} 2013, \aap, 560, A66

\bibitem[Rigault et al.(2015)]{rigault2015} Rigault, M., Aldering, G., Kowalski, M., et al.\ 2015, \apj, 802, 20

\bibitem[Rigault et al.(2018)]{rigault2018} Rigault, M.,
  Brinnel, V., Aldering, G., et al.\ 2018, arXiv:1806.03849
% S
\bibitem[Scolnic et al.(2018)]{scolnic2018} Scolnic, D.~M., Jones, D.~O., Rest, A., et al.\ 2018, \apj, 859, 101

% T
% U 
% V
% W
\bibitem[Wong et al.(2019)]{wong2019} Wong, K.~C., Suyu, S.~H., Chen, G.~C.-F., et al.\ 2019, arXiv e-prints, arXiv:1907.04869

% X
% Y
 Z
\end{thebibliography}
